Analysis Stand Features 

### 2017-05-15 analysis/analysis_stand_features.Rmd
close sink et al

  file_out <- file(paste0(di,'out/anovas_competition/aov_', i, '.txt'))
  sink(file_out)
  cat("MODEL \n")
  print(out$mymodel) 
  cat("\n")

@@

  sink()
  close(file_out)
}
```

@@

  file_out <- file(paste0(di,'out/anovas_topo/aov_', i, '.txt'))
  sink(file_out)
  cat("MODEL \n")
  print(out$mymodel) 
  cat("\n")

@@

  sink()
  close(file_out)
}
```

>>>>

  out <- get(paste0('aov_', i))
  file_out <- file(paste0(di,'out/anovas_competition/aov_', i, '.txt'), "w")
  sink(file_out)
  cat("MODEL \n")
  print(out$mymodel) 
  cat("\n")

@@

  while (sink.number()>0) sink()
  # close(file_out)
}

while (sink.number()>0) sink()
```

@@

  file_out <- file(paste0(di,'out/anovas_topo/aov_', i, '.txt'), "w")
  sink(file_out)

  cat("MODEL \n")
  print(out$mymodel) 
  cat("\n")

@@

  while (sink.number()>0) sink()
  # close(file_out)

while (sink.number()>0) sink()
```
